\documentclass{article}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{fontspec}
\usepackage{tcolorbox}
\usepackage{underscore}
\usepackage{verbatim}
\usepackage{minted}
\usemintedstyle{rainbow_dash}
\setminted{breaklines}
\pagestyle{empty}
\begin{document}
\section*{Experiment \jobname}
\subsection*{\textbf{Title:} Study and Implementation of:}
\begin{itemize}
	\item Sub queries
	\item Views
\end{itemize}
\subsection*{\textbf{Objective:}}
\begin{itemize}
	\item To perform nested queries and joining queries using DML commands
	\item To understand the implementation of views
\end{itemize}
\subsection*{Lab Assignment}
\begin{itemize}
	\item Find all information of sailors who have reserved boat number 101.
	\item Find the name of boat reserved by Bob.
	\item Find the names of sailors who have reserved a red boat, and list in the order of age.
	\item Find the names of sailors who have reserved at least one boat.
	\item Find the ids and names of sailors who have reserved two different boats on the same day.
	\item Find the ids of sailors who have reserved a red boat or a green boat.
	\item Find the name and the age of the youngest sailor.
	\item Count the number of different sailor names.
	\item Find the average age of sailors for each rating level.
	\item Find the average age of sailors for each rating level that has at least two sailors.
\end{itemize}
\subsection*{Code}
\inputminted{sql}{code/\jobname.sql}
\subsection*{Output}
\verbatiminput{output/\jobname.txt}
\end{document}
